ASTR480 Final Report:\\ \textit{Asteroids in TESS}

### 2024-09-06 FinalReport/FinalReportDraft.tex
cut with a bkg limit

@@

\subsection*{Period detection}\label{SubSec:Periods}

@@

There are a few different implementations of a Lomb-Scargle periodogram available in world of astronomy python packages.
I first tried using the \texttt{Lightkurve} \citep{Lightkurve2018} package built for period analysis of TESS (and Kepler) data of variable stars.
\texttt{Lightkurve} was easy to use but didn't allow for fine-tuning of the periodogram, or give any model of the curve it produced.
Peeling back a layer of abstraction and using the Lomb-Scargle periodogram as implemented by \texttt{Astropy}\citep{Astropy2022} was the next option.
There were interesting similarities and differences between the packages.
\texttt{Lightkurve} is based on the \texttt{Astropy} methods, but does not give all the functionality, instead opting to simplify the process.
\texttt{Astropy} gives a statistic on how confident it is in the detected frequency is, the false alarm probability.
It also returns a model, in the form of

>>>>

%TODO YORP spin up

@@

\subsection{Period detection}\label{SubSec:Periods}

@@

There are a few different implementations of a Lomb-Scargle periodogram available in world of astronomy python packages.
I first tried using the \texttt{Lightkurve} \citep{Lightkurve2018} package built for period analysis of TESS (and Kepler) data of variable stars.
\texttt{Lightkurve} was easy to use but didn't allow for fine-tuning of the periodogram, or give any model of the curve it produced.
The next option was peeling back a layer of abstraction and using the Lomb-Scargle periodogram as implemented by \texttt{Astropy}\citep[\citet{Astropy2022} but see][for the implementation]{Vanderplas2012,Vanderplas2015}. 
There were interesting similarities and differences between the packages.
\texttt{Lightkurve} is based on the \texttt{Astropy} methods, but does not give all the functionality, instead opting to simplify the process.
\texttt{Astropy} gives a statistic on how confident it is in the detected frequency is, the false alarm probability.
It also returns a model, in the form of
